% TeX_root = ../main.tex

\marginnote{\scriptsize 01/04/2025 }

\begin{definition}
  Let $V, W$ be normed spaces. A crossed norm on $V \otimes W$ is a
  norm satisfying $ \|v \otimes w\| \le \|v\| \|w\|$.
\end{definition}
\begin{definition}
  Let $X, Y$ be normed spaces. A tensor norm on $X \otimes Y$ is a
  crossed norm such that $ X^* \otimes Y^* \subset (X \otimes Y)^*$,
  and $ \|\phi \otimes \psi\| \le \|\phi\| \|\psi\|$ for all $ \phi
  \in X^*, \psi \in Y^*$.
\end{definition}

\begin{lemma}
  If $\|\cdot\|$ is a tensor norm on $X \otimes Y$, then
  \begin{align*}
    \|x \otimes y \| = \|x\| \|y\| \\
    \|\phi \otimes \psi \| = \|\phi\| \|\psi\|
  \end{align*}
  for all $x \in X, y \in Y, \phi \in X^*, \psi \in Y^*$.
\end{lemma}
\begin{proof}
  \textcolor{red}{Exercise}
\end{proof}

Recall that the projective norm is a tensor norm and it is the
largest. Also recall that injective norm is a tensor norm, which is
the smallest.

\begin{theorem}
  If $Z \leqslant X$, then
  \begin{align*}
    Z \check{\otimes} Y \leqslant X \check{\otimes} Y
  \end{align*}
\end{theorem}
\begin{proof}
  Immediate from the definition of the injective tensor norm.
\end{proof}

Moreover note that $X \otimes Y$ has an injection to
$\textrm{Bil}(X^* \times Y^*)$ as evaluations. Also note that
$\textrm{Bil}(X^* \times Y^*)$ has a norm where $\phi \in
\textrm{Bil}(X^* \times Y^*)$ has norm
\begin{align*}
  \|\phi\| = \sup\{|\phi(x, y)| \ : \ \|x\|, \|y\| \le 1\}
\end{align*}
Then the push-back norm into $X \otimes Y$ is the injective tensor norm.

If instead $X \otimes Y$ borrows the norm via the injection $X
\otimes Y \hookrightarrow \textrm{Bil}(X \times Y)^*$ again via the
\textcolor{red}{obvious injection}. This push-back gives the
projective tensor norm.

Recall that $(X \hat{\otimes} Y)^* = \textrm{Bil}(X \times Y)$

\begin{theorem}
  Let $\rho \in \textrm{Bil}(X \times Y)$. Then, $\rho \in (X
  \check{\otimes} Y)^*$ iff there is a radon measure (from Reisz
  representation) $\mu$ in
  $X^*_1 \times Y^*_1$ such that $$\rho(x \otimes y) = \int_{X^*_1 \times
  Y^*_1}  \phi(x) \psi(y) \ d  \mu(\phi, \psi)$$
  In this case, we say $\rho$ is an integral Bilinear map.
\end{theorem}
\begin{proof}
  Use $z \to f_z: $
\end{proof}

\begin{definition}
  Let $X, Y$ be Banach spaces. Let $\alpha$ be a tensor norm on $X
  \otimes Y$. We define the dual norm $\alpha^*$ on $ X^* \otimes Y^*
  $ via the embedding
  \begin{align*}
    X^* \otimes Y^* \hookrightarrow (X \otimes Y)^*
  \end{align*}
\end{definition}

\begin{lemma}
  $\alpha^*$ is a tensor norm.
\end{lemma}

\begin{definition}
  Let $\Xi : X \otimes Y \to Y \otimes X$ be the flip map. The flip
  of $\alpha$ denoted $\alpha_f$ is $\alpha \circ \Xi$.
\end{definition}

clearly the projective and injective norms are flip invariant.

\begin{exercise}
  Let $X, Y$ be finite dimensional normed spaces. Then
  \begin{enumerate}[label=(\arabic*)]
    \item $\wedge^* = \vee$ and $\vee^* = \wedge$
    \item $(\alpha^*)^* = \alpha$
  \end{enumerate}
\end{exercise}
\begin{proof}
  \begin{enumerate}[label=(\arabic*)]
    \item
    \item
      Let $\rho \in X^* \otimes Y^*$. By definition,
      \begin{align*}
        \|\rho\|_{\wedge^*} &= \sup \{ |\rho(z)| \ : \ z \in (X
        \hat{\otimes} Y)_1 \} \\
        &\ge \|\rho\|_{\vee} \\
        &= \sup \{ \rho(x \otimes y) \ : \ x \in X_1, y \in Y_1 \}
      \end{align*}
      Let $\varepsilon >0$, and let $z = \sum_{i = 1}^{N} x_i \otimes
      y_i \in (X \otimes Y)_1$
      be such that $\|z\|_{\wedge} > \sum_{i = 1}^{n} \|x_i\|\|y_i\|
      - \varepsilon$ and $\sum_{i = 1}^{n}  \rho(x_i \otimes y_i) = \rho(z)
      \ge \|\rho\|_{\wedge^*} - \varepsilon$. Then
      \begin{align*}
        \sum_{i = 1}^{n}  \rho(x_i \otimes y_i) \le \|\rho\|_{\wedge}
        \sum_{i = 1}^{n} \|x_i\|\|y_i\| \le \|\rho\|_{\wedge}()
      \end{align*}
  \end{enumerate}
\end{proof}
